Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact

### 2019-06-02 tse19/main.tex
pass up to description of RQs

\IEEEraisesectionheading{
\section{Introduction}
\label{sec:introduction}}

@@

\Mar{Sotero, por favor, verifique que os numeros que estao aparecendo
  no texto (usados nas macros) estao corretos! Vc. nao precisa
  atualizar o ingles, mas se os dados nao estiverem corretos e vc. nao
  explicar as mudanca (em portugues mesmo) nao vamos ter condicoes de
  revisar.}
\textcolor{red}{[S.J: Ok.]}
We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria:\Mar{alguma restricao
  sobre o numero minimo de testes por projeto?$\rightarrow$}  \textcolor{red}{[S.J: Nao, mantemos as mesmas restricoes por ordem descendentes das stars]} (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}\Mar{ver comentario abaixo}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that one hundred stars was enough to eliminate trivial subjects. The
third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from repository
statistics (\eg, number of forks, main programming language); it does
not provide a feature to search for projects containing certain files
(\eg{}, \emph{pom.xml}) in the directory structure. 
\Mar{Sotero, vc. usou ou nao usou este recurso da API do GitHub? Estou muito cofuso
  aqui (por isto tive que interromper revisao). Se vc usou, este
  quarto criterio precisa sair e entrar outro dizendo
  explicitamente que usamos isto. Fora isto, logo abaixo vc. diz que
  de um total de 4111, 3154 *nao* eram Maven. Mas, como eh possivel,
  se vc. garante (atraves deste recurso) a presenca de um arquivo pom.xml?}

\textcolor{red}{[S.J: Tivemos dois momentos, o primeiro momento, usamos os mesmos criterios e script do paper ase17 para minerar os subjects. No segundo momento, usamos uma library python chamado PyGithub, ``https://github.com/PyGithub/PyGithub``, para gerenciar recursos do Github API. Utilizamos a funcao search\_code, que busca por especifico arquivo em repositorios ``pygithub.search\_code(pom in:pom.xml filename:pom.xml,order=desc)``, curl Github API ``https://api.github.com/search/code?q=pom in:pom.xml+filename:pom.xml``, e em seguida filtramos esses subjects com os crietrios (2) e (3) do paper.    
]}

Figure~\ref{fig:subject-query} illustrates the query to the \github{}
API as an HTTP request.   The result set is sorted
in descending order of stars.

\begin{figure}[t!]
\centering
\tiny
\lstset{
    escapeinside={@}{@},
    numbers=left,xleftmargin=1em,frame=single,framexleftmargin=0.5em,
    basicstyle=\ttfamily\scriptsize, boxpos=c, numberstyle=\tiny,
    showstringspaces=false
}
\begin{lstlisting}
https://api.github.com/search/repositories?q=language:java
 +stars:>=100+pushed:>=2016+mvn%20in:readme&sort=stars
\end{lstlisting}
  \vspace{-3mm}
  \caption{\label{fig:subject-query} Query to the \github{} API for
  projects that (1) use Java, (2) contains at least 100
  stars, (3) has been updated on January 1st, 2016 (or later), (4) \Fix{contains
  the string \emph{mvn} in the \emph{readme} file.}\Mar{Please revise.}}
  \vspace{-3mm}
\end{figure}

We used the following methodology to select projects for analysis. After obtaining the list of potential projects from GitHub, we
filtered those
containing a \pomf{} file in the root directory.\Comment{  A Maven project may
contain several sub-modules with multiple \pomf{} files.}
Then, considering this set of Maven projects, we
executed the tests for \SubjectsReruns{} times to discard those projects with
issues
in the build file and non-deterministic results observed from sequential
executions.
As of March 5th 2019, our search criteria returned a total of
\SubjectsGithub{}
subjects.
From this set of projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, 
\SubjectsGithubNotTestable{} projects were not considered because of
environment incompatibility
(\eg, missing\Comment{ required web browser or database management
system}~DBMS),
\SubjectsGithubFlaky{} projects were discarded because of
``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes
or fails under
the same circumstances leading to non-deterministic results.
As some of our experiments consist of running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
From the remaining \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with \SuiteFailingThreshold{} or more failing tests as to
reduce bias. For the
remaining projects with failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to ignore failing tests.
Our final set of subjects contains \numSubjs{} projects. 
 \textcolor{red}{[S.J: Foi possivel observar que houve uma consideravel conversao de ferramenta de automacao, do Maven para Gradle,  dos 3154 subject que nao eram Maven, 2302 eram Gralde (73\%). Projeto como o MapDB, que e bastante citado no paper de ase17, atualmente converteu-se a Gradle. ]}

 Figure~\ref{fig:subjects} summarizes our sample set.

\begin{figure}[ht]
  \vspace{-5mm}
  \centering
  \includegraphics[width=0.37\textwidth]{results/piechart-subjs.pdf}
  \caption{\label{fig:subjects}We fetched \SubjectsGithub{} popular projects
  hosted on \github{}. From this initial sample, we ignored
  \SubjectsGithubNotMaven{} projects without Maven support,
  \SubjectsGithubNotTestable{} with missing dependencies,
  \SubjectsGithubFlaky{} projects with flaky tests, and
  \SubjectsGithubTooManyFailures{} projects had at least
  \SuiteFailingThreshold{} of failing tests. We considered
  \numSubjs{} projects to conduct our study.\Mar{Sotero, este plot e
    macros estao atualizados?}} \textcolor{red}{[S.J:Atualizado.]}
\end{figure}

@@

\Mar{Por que isto esta em uma secao ``Objects of Analysis''? Eh esta
  mesmo a configuracao de maquina que vc. usou.} \textcolor{red}{[S.J:Atualizado.]}
To run our experiments, we used a Intel Xeon ES-2650 v4 (2.20 GHz)
with eight virtual CPUs (four cores with two native threads each) and
16GB of memory, running Ubuntu 18.10 Cosmic Cuttlefish (64-bit version).  We
used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test
suites. To process test results and generate plots we used Python\Comment{ 3.4},
Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are publicly available for
replication on our website~\cite{ourwebpage}.  This includes supporting
scripts\Comment{ (\eg, the scripts to run the tests and generate raw analysis
data)} and the full list of projects.

@@

We pose the following research questions, organized by the dimensions
of analysis we presented in Section~\ref{sec:intro}.

@@

>>>>

\IEEEraisesectionheading{
\section{Introduction}\label{sec:introduction}}

@@

\begin{figure}[t]
%  \vspace{-5mm}
  \centering
  \includegraphics[width=0.37\textwidth]{results/piechart-subjs.pdf}
  \caption{\label{fig:subjects}Breakdown of project by sources of
    issues.}
\end{figure}

@@

We used the Python library PyGitHub~\Fix{cite}, which uses the
\github{}'s search API~\cite{githubsearch}, to identify projects that
satisfy the following criteria: (1) the primary language is
Java\footnote{In case of projects in multiple languages, the \github{}
  API considers the predominant language as the primary language.},
(2) the project has at least 100 stars, and (3) the latest update was
on or after January 1st, 2016. Although there is no clearcut limit on
the number of \github{} stars~\cite{github-stars} to define relevant
projects, we observed that one hundred stars was enough to eliminate
trivial subjects. The third criteria serves to skip projects without
recent activity.

To sum up, after obtaining the list of potential projects from GitHub,
we filtered those containing a \pomf{} file in the root
directory.\Comment{ A Maven project may contain several sub-modules
  with multiple \pomf{} files.}  Then, considering this set of Maven
projects, we executed the test suite for \SubjectsReruns{} times
discarding those projects with issues. Figure~\ref{fig:subjects}
shows the breakdown of projects by source of issue. As of
March 2019, our search returned a total of \SubjectsGithub{}
subjects.  We found that \SubjectsGithubNotMaven{}
projects in this set were not Maven. Compared with our previous
experiment~\cite{Candido:2017:TSP:3155562.3155667}, executed nearly 2
years ago, we observed  that many more
projects now use Gradle---73\% of the \SubjectsGithubNotMaven{} non-Maven
projects use Gradle. Although parallelization can
be used in Gradle, we decided to keep using using Maven for
consistency with the previous experiment. From the remaining set of
projects, \SubjectsGithubNotTestable{} were discarded
because of environment incompatibility (\eg, missing\Comment{ required
  web browser or database management system}~DBMS) and
\SubjectsGithubFlaky{} projects were discarded because of flaky
tests~\cite{luo-etal-fse2014}. A flaky test is a test that passes or
fails non-deterministically resulting in wasted effort.  As some of our experiments consist of running tests on
different threads, we ignored these projects as it would be
impractical to identify whether a test failed due to a race condition
or some other source of flakiness. Note that existing techniques exist to
detect and mitigate flakiness~\Fix{cite cite}, so we considered this
problem out of scope. From the remaining
\SubjectsGithubConsistant{} projects with test execution
manifesting deterministic results, we
eliminated \SubjectsGithubTooManyFailures{} projects that contain
\SuiteFailingThreshold{} or more failing tests as to reduce
bias. For projects with less failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to discard the failing tests as we did not
want a premature termination of test run to influence in timings.  Our final set of
subjects include  \numSubjs{} projects.

 %% \textcolor{red}{[S.J: Foi possivel observar que houve uma consideravel conversao de ferramenta de automacao, do Maven para Gradle,  dos 3154 subject que nao eram Maven, 2302 eram Gralde (73\%). Projeto como o MapDB, que e bastante citado no paper de ase17, atualmente converteu-se a Gradle. ]}

@@

We pose the following research questions, organized by the dimensions
of analysis we presented in Section~\ref{sec:introduction}.

@@

To run our experiments, we used an Intel Xeon ES-2650 v4 (2.20 GHz)
with eight virtual CPUs (four cores with two native threads each) and
16GB of memory, running Ubuntu 18.10 Cosmic Cuttlefish (64-bit version).  We
used\Comment{ Git,} Java 8 and Maven 3.3.9 to build projects and run test
suites. To process test results and generate plots we used Python\Comment{ 3.4},
Bash, R and Ruby\Comment{ 2.3}.  All source artifacts are publicly available for
replication on our website~\cite{ourwebpage}.  This includes supporting
scripts\Comment{ (\eg, the scripts to run the tests and generate raw analysis
data)} and the full list of projects.
